Identification and Spatial Analysis of Law Firms Naming Patterns in Russia Using Text Embeddings

### 2025-01-28 law-firms-names/Paper.Rmd
Edit methods, results, discussion, conclusion, figures, abstract, and style, before submitting the second revision, #4

---
title: "Identification and Spatial Analysis of Law Firms Naming Patterns in Russia Using Text Embeddings"
author: "Pavel Syomin"
output:
  word_document:
    reference_doc: "journal-article/reference.docx"
bibliography: "journal-article/refs.bib"
csl: "journal-article/apa.csl"
link-bibliography: False  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE, 
  echo = FALSE, 
  fig.width = 4.96, 
  fig.id = FALSE,
  dpi = 1200)
IS_PAPER <- TRUE # used in script to disable saving of names and samples
```

@@

```{r data-imports, cache=TRUE, include=FALSE}
source(here("journal-article", "Script.R"))
```

@@

**Abstract:** The present study analyzes law firm naming in Russia, with a particular focus on the geographical aspects of this phenomenon. The primary objective of this research is to ascertain the impact of the spatial relations between the country's regions, specifically those of a neighboring, proximity, and belonging to a parent-level subdivision, on the naming of law firms. To conduct the analysis, data regarding law firms is extracted from the open dumps of the state registry of small and medium-sized businesses. The names of the firms are transformed into numerical vectors, subsequently clustered with the KMeans method, and then manually grouped to identify naming strategies. Numerical representations of law firm names within each region are averaged to get region embeddings, which are then used to compare the names of law firms in different regions. The research findings indicate that regions situated closer to one another or sharing a common border tend to adopt slightly more similar law firm names. Furthermore, regions that are part of the same economic region also display a greater degree of similarity in law firm naming. Three primary strategies of law firm naming are “Form”, “Law“, and “Service”. Volga and North Caucasus economic regions are characterized by the predominance of the “Service” strategy, whereas the Volga-Vyatka economic region exhibits a “Law” strategy, and the remaining territories demonstrate a combination of naming strategies. The results of the study lend support to the widely used classification of economic regions in Russia. The findings also underscore the impact of neighboring, proximity, and interconnectivity on the economic and cultural attributes of the regions. The administrative open data processing techniques, as well as the methods of working with firm names based on neural networks proposed in this paper, may be used by other economic geographers for their own research purposes.

@@

Law firm names can follow different patterns. A naming pattern can be defined as as a typical way of branding, identified by the use of identical or semantically similar words or phrases. For instance, the names “Law firm “Femida” and “Law company “Alibi” follow one pattern, while “Centre of legal aid and support” is an example of another. Patterns can be grouped several times to form a hierarchical classification [@Anora2015]. Such a classification can help to identify naming strategies. Compared to patterns, strategies are broader groups of names, usually based on a common purpose, e.g. highlighting a company's affiliation to a certain activity (retail, banking, transport, education, etc). @BassolsiGardella2023 propose a two-dimensional Strategic Naming Model (SNM) that includes two pairs of opposing strategies: belonging and uniqueness, no-strategy and market. They discover a difference between three Colombian cities in the naming strategies of their tourism companies. It is likely that such a variation is not be limited to the cities of Colombia and the tourism industry and can also be found in the case of law firms in Russia.

@@

@@

## 2.2. Methods

### 2.2.1. Law firms selection criteria

@@

### 2.2.2. Firm data acquisition

@@

### 2.2.3. Firm name embeddings retrieval

@@

### 2.2.4. Naming patterns identification and classification

@@

The resulting clusters are then manually grouped. A random sample of 20 names is selected from each cluster. With 50 clusters and 20 sampled names allocated in each, the total size of the dataset for manual processing is 1, 000. The cluster samples are carefully examined, and a concise description is provided for each, e.g. “Names with the word “консалт/консалтинг” (consult/consulting)”. After this, the clusters are examined again and assigned to a naming pattern, e.g. “Consulting” or “Law firm”. Finally, the clusters and their naming patterns are divided into four previously mentioned naming strategies derived from @BassolsiGardella2023. Each cluster belongs to a single pattern, and each pattern belongs to a single strategy. Each strategy consists of several patterns, and each pattern consists of one or many clusters, forming a hierarchical structure.

Each group except for the “Misc” category represents a specific naming strategy. The “Form” strategy encompasses names that are based on a word or words denoting a kind of business entity, including “company”, “firm”, “group”, “partnership”, “center”, “alliance”, and “corporation”. The “Law” strategy emphasizes the firm's affiliation with the legal services market, employing terms such as “legal”, “juridical”, “lex”, “law”, and “lawyer”. Names belonging to the “Service” strategy may indicate a particular service provided by a law firm (“advisor”, “consulting”, “protection”, “support”, “warrant”), describe the sectors of businesses the firm is primarily engaged with (“technology”, “development”, “house management”, “accounting”), or mention services in general. The “Misc” category is a catch-all group for names that do not clearly align with any other category.

### 2.2.5. Spatial regularities identification

Analysis of autocorrelation is used to check whether the spatial distribution of names belonging to each cluster identified on the previous step is random or has some regularities. Regions (constituent entries) or the Russian Federation were selected as a spatial subdivision for calculating the autocorrelation measures. It could have been more reasonable to use the next spatial level, municipal territories, to perform the computations, but exploratory data analysis has shown that a lion's share of such territories has no law firms, because the legal business is highly concentrated in cities and large settlements.

Six spatial weights matrices are used to ensure the robustness of the results. Three of these matrices are constructed with K nearest neighbours technique based on the location of region's centroids, where K equals 3, 4 or 6, respectively. Another matrix also uses geographical properties of regions, but instead of centroids, it relies on the existence of common border lines or points to identify neighbouring regions. Sakhalin and Kaliningrad regions, being enclaves and thus having zero immediate neighbors, were manually connected with a few closest regions. Two remaining matrices treat regions belonging to the same upper-level metaregion as neighbours, and all the other regions as non-neighbours. For one of these two matrices, economic regions act as metaregions, and for another, federal districts are used in this fashion. Economic regions are defined according to the classification widely used by economic geographers and spatial development practitioners in Russia for decades and outlined, for example, in [@Leyzerovich2010]. Federal districts composition is defined in the Executive Order of the President of Russia No. 849, Dated May 13, 2000, “On the Plenipotentiary Representative of the President of the Russian Federation in the Federal District” (with up-to-date amendments).

For each cluster, a global Moran's I metric is calculated. The variable of interest is a share of law firm names belonging to the cluster in a total quantity of law firm names in a region. If there are no law firm names of the cluster in the region, the share is considered to equal zero. P-values are adjusted for multiple comparisons with Holm's correction. Significance level (alpha) is set to 0.05.

For the clusters with statistically significant global Moran's I, a local Moran's I was subsequently calculated. P-values are adjusted with local Holm's correction. Cluster classification of local Moran's I are mapped.

### 2.2.6. Data statistics

@@

## 3.1. Law firms naming strategies

Law firm names clusters resulted from UMAP → DBSCAN pipeline are illustrated using scatterplot in Fig. 1. The visual quality of clusterisation is high: all the clusters are compact, round, and separated by considerable gaps. There are no noise points, and all the names have been easily assigned to clusters.

```{r fig-1-clusters, fig.cap="**Fig 1.** Law firm names clusters resulting from UMAP → DBSCAN processing of law firm names embeddings. Numbers are assigned automatically by DBSCAN", fig.height=4}
clusters_plot
```

```{r table-1-clusters}
kable(
  clusters_info_table,
  col.names = c(
    "# of cluster", "# of names", "Description",
    "Category", "Strategy"
  )
)
```

Table 1 shows cluster sizes and sample names from the clusters with manually assigned short cluster descriptions, categories and strategies. The quantity of clusters (52) is relatively big, and their size is not even: while the largest group of names consists of items, the smallest one includes just 12 objects. Almost 1/3 of clusters (17) is comprised of a mixture of short (usually a single-word) names that cannot be given a reasonable description. They are marked as “Misc” and classified as “No-strategy”.

All the other names are split between three primary strategies. “Market” strategy is comprised of firms with names having generally positive connotations in Russian language that help to pursue a potential client in a high quality of legal aid and thus act as a some sort of advertisement (“Guarantor”, “Expert”, “Partnership”, “Helper”, "Center” categories and some others). “Belonging” strategy, as its name suggests, make a strong emphasis on their belonging to the legal services market by using the words “law”, “lawyer”, “legal” or various Russian equivalents of “law firm” phrase. A distinct category of law firms with this strategy is formed by organisations that use a personal branding that follow the broad pattern “(law firm) <last name of a person> with partners” where (law firm) is an optional part, and <last name of a person> is a pointer to a featured lawyer of this organisation. Even if “law firm” subpart of the firm name is optional, the entire pattern is strongly associated in Russia with lawyers, thus this type of firm naming marks the belonging to the legal services sphere. Finally, “Uniqueness” strategy encompasses companies with names mentioning a particular kind of legal services (e.g. “Consulting”), or a target customers group (e.g. “Business”), or a related area of specialization (real estate, finance, audit, development), or a specific geographic location.

```{r table-2-strategies-summary}
kable(
  strategy_counts,
  digits = c(NA, 0, 0),
  col.names = c("Strategy", "# of names", "%")
)
```

Among the strategies, “No-strategy” (i.e. the absence of a clear strategy) is the most popular (see Table 2). It encompasses more than 1/3 of all the studied names. Belonging strategy is the second by the popularity holding 30% of law firms. Uniqueness strategy is employed by approximately 20% of companies, and the least typical one, market strategy, is used by slightly more than 10% of law firms.

@@

As Tables 3 and 4 demonstrate, there are few law firm names clusters with some regularities in the spatial distribution of law firm names. These two tables display results only for the clusters where global Moran's I coefficient is statistically significant. The values of Moran's I metric for all the other clusters are close to zero, and their adjusted p-value is above the selected threshold of 0.05, so the results for these clusters are not shown for brevity.

```{r table-3-moran-i-by-neighborhood}
moran_test_by_regions %>% 
  filter(p_adj < 0.05) %>% 
  kable(
    digits = c(0, NA, 2, 3),
    col.names = c("# of cluster", "Description", "Moran's I", "Adj. p-value")
  )
```

```{r table-4-moran-i-by-economic-regions}
moran_test_by_er %>% 
  filter(p_adj < 0.05) %>% 
  kable(
    digits = c(0, NA, 2, 3),
    col.names = c("# of cluster", "Description", "Moran's I", "Adj. p-value")
  )
```

According to the autocorrelation analysis results in both branches, there are in total four law firm names clusters where the spatial distribution is different from the random. One of these clusters, “Center or company with geographical location”, is present in both tables and is characterized by the highest value of Moran's I, that is about 0.66. Thus, it is likely that law firms with names mentioning a geographical location of the country are not distributed randomly within the country, but situated in a number of neighbouring regions. Two maps on the Fig. 2, despite several differences, demonstrate that it is the regions in Eastern and Western Siberia that are characterized by the highest concentration of “geographically referenced” law firm names. A brief manual investigation uncovers that such names usually reference a particular region (e.g. Altai), or a specific city (e.g. Krasnoyarsk), or entire geographical area as a whole (Siberia). This argues for the presence of some sort of local or regional identity which is of highest expression in Siberia. It is possible that similar geo-based naming is present in other parts of the country, but the automatic clusterisation of law firm names using their embeddings cannot handle them properly — either because the quantity of geolocated names in other parts of the country is substantially smaller or because the text vectors do not reflect the similarity between the Siberian geographical mentions and geographical mentions in the other parts of Russia. Overall, an issue of geolocated law firm names is intriguing and requires further investigation.

As for other clusters with statistically significant global Moran's I (“Forensic” names, “Experts and advisors”, and personal-branding pattern), the hotspots are situated in the European South of Russia. In the case of “Forensic” names, it is likely to be attributed to a tiny set of national republics of North Caucasus that are probably outliers, because their overall number of law firms and the distribution of naming strategies is substantially different from the one in the majority of regions. “Experts and advisors” cluster demonstrates hotspots in Rostov, Volgograd and Astrakhan regions. They are characterized by a relatively high number of law firms and thus cannot be left to as just outliers. However, the exact reasons for the spatial concentration of this naming pattern in these regions remains unclear. Finally, a personal branding cluster represents a drastic split of the European South into two groups of regions: the first one comprising of several national republics with high level of personal branding names and the second one consisting of some other national republics and all the regular regions with small share of such names. This may be seen as a slight argument for a position that European South of Russia is a conglomerate of two quite distinct groups of regions.

@@

The findings of the study are somewhat contradictory. On the one hand, several hypotheses have been proven. These include the following: law firm names in neighboring regions are more similar than law firm names in non-neighboring regions; the smaller the geographic distance between regions, the more similar the law firm names; and law firm names within an economic region are typically more similar compared to the law firm names outside an economic region. On the other hand, the difference in the metrics of similarity is relatively small in each case, as is the correlation coefficient. It is therefore important to note that although the postulated phenomena do indeed exist, their magnitude is weak.

The three principal strategies for naming law firms are as follows: “Form”, “Law”, and “Service”. The first of these represents a minority approach, while the remaining majority is divided between two other strategies. In the European South of Russia and in the Volga economic region, “Service” is a dominant strategy. However, no other spatial patterns in law firms naming have been identified. Economic regions are typically characterized by a mixture of naming strategies, except for Volga-Vyatka, where the “Law” strategy prevails, and Volga and North Caucasus, where the “Service” strategy is dominant.

The contribution of this study is primarily theoretical and methodological in nature. It underscores the significance of firm names as a source of information for business- and economy-related research. It also proposes a technique for comprehensive analysis of branding in a geographical context through the use of modern natural language processing (NLP) solutions based on artificial neural networks. Additionally, it advocates for the utilization of disaggregated administrative open data for a spatial analysis. The findings demonstrate the effect of geographical proximity, neighboring, and economic relations on the similarity of the economic and, to a certain extent, cultural properties of the territories represented in firm names. The results generally align with the widely accepted classification of economic regions in Russia, although they highlight a few instances where a theoretically undesired internal heterogeneity within an economic region is observed. Finally, the study provides an illustration of a semi-automated brand classification within a specific economic sector and discovers a geographical variation in naming strategies that could be further investigated.

@@

>>>>

---
title: "Identification and Spatial Analysis of Law Firms Naming Patterns in Russia Using Text Embeddings"
author: "Pavel Syomin"
output:
  word_document:
    reference_doc: "journal-article/reference.docx"
bibliography: "journal-article/refs.bib"
csl: "journal-article/apa_numeric.csl"
link-bibliography: False  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE, 
  echo = FALSE, 
  fig.width = 6.7, 
  fig.id = FALSE,
  dpi = 1200)
IS_PAPER <- TRUE # used in script to disable saving of names and samples
```

@@

```{r data-imports, cache=TRUE, include=FALSE}
source(here("journal-article/Script.R"))
```

@@

**Abstract:** The present study analyzes the naming of law firms in Russia, with a particular focus on the geographical aspects of this phenomenon. The main objectives of this research are to identify law firm naming patterns, to categorise them and to test whether there are any spatial regularities in the distribution of law firms according to the identified patterns. To conduct the analysis, data regarding law firms is extracted from the open dumps of the state registry of small and medium-sized enterprises. The names of the firms are transformed into numerical vectors, subsequently clustered with the KMeans method, and then manually grouped to identify naming patterns and strategies. Global and local Moran's *I* statistics are calculated to test for spatial autocorrelation in the proportion of a given pattern in the regions. As a result, 22 naming patterns are identified, grouped into four naming strategies. Apart from no-strategy (40% of law firms), the most popular strategy is belonging (to the legal services market — 30%), followed by uniqueness (of service or location — 20%) and market (words and phrases with positive or promotional meaning — 10%). The research findings indicate that the spatial distribution of law firm naming patterns is generally not significantly different from random, with two exceptions: geographical branding in Siberia and an unusual heighborhood of regions with high and low proportions of “Expert” and “Personal brand” patterns in the European South.

@@

Law firm names can follow different patterns. A naming pattern can be defined as as a typical way of branding, identified by the use of identical or semantically similar words or phrases. For instance, the names “Law firm “Femida” and “Law company “Alibi” follow one pattern, while “Centre of legal aid and support” is an example of another. Patterns can be grouped several times to form a hierarchical classification [@Arora2015]. Such a classification can help to identify naming strategies. Compared to patterns, strategies are broader groups of names, usually based on a common purpose, e.g. highlighting a company's affiliation to a certain activity (retail, banking, transport, education, etc). Bassols i Gardella et al. [@BassolsiGardella2023] propose a two-dimensional Strategic Naming Model (SNM) that includes two pairs of opposing strategies: belonging and uniqueness, no-strategy and market. They discover a difference between three Colombian cities in the naming strategies of their tourism companies. It is likely that such a variation is not be limited to the cities of Colombia and the tourism industry and can also be found in the case of law firms in Russia.

@@

Russia belongs to the Germanistic branch of a civil law legal system. Legal services (advice, negotiation, representation in court, etc) for organisations and individuals are usually provided by private law companies and individual lawyers. The market is divided between ordinary lawyers and advocates (members of the Bar), but there is no bar monopoly. There are ~90, 000 law firms in Russia, including ~40, 000 commercial law companies, ~30, 000 sole practitioners, ~20, 000 bar (advocate) offices, and ~10, 000 bar (advocate) organisations. There are no geographical restrictions on legal practitioners, so that a law firm registered in one region of the country can provide services in any other region. There are full-service and specialised law firms, as well as Russian law firms (the majority) and foreign law firms (the influential minority).

@@

## 2.3. Methods

### 2.3.1. Law firms selection criteria

@@

### 2.3.2. Firm data acquisition

@@

### 2.3.3. Firm name embeddings retrieval

@@

### 2.3.4. Naming patterns identification and classification

@@

The resulting clusters are then manually grouped. A random sample of 20 names is selected from each cluster. With 50 clusters and 20 sampled names allocated in each, the total size of the dataset for manual processing is 1, 000. The cluster samples are carefully examined, and a concise description is provided for each, e.g. “Names with the word “консалт/консалтинг” (consult/consulting)”. After this, the clusters are examined again and assigned to a naming pattern, e.g. “Consulting” or “Law firm”. Finally, the clusters and their naming patterns are divided into four previously mentioned naming strategies derived from Bassols i Gardella et al. [@BassolsiGardella2023]. Each cluster belongs to a single pattern, and each pattern belongs to a single strategy. Each strategy consists of several patterns, and each pattern consists of one or many clusters, forming a hierarchical structure.

### 2.3.5. Testing for spatial regularities

Spatial autocorrelation analysis is used to check whether the spatial distribution of names following each pattern identified in the previous step is random or has some regularities. Regions (constituent entities) of the Russian Federation are chosen as the unit of observation. Municipal territories, the next level of spatial division, are not used, because an exploratory data analysis has shown that the lion's share of such the spatial units do not have any law firms.

Six spatial weight matrices are utilized to ensure the robustness of the results. Three of these matrices are constructed using the K-nearest neighbors technique, where K is 3, 4 or 6. Another matrix relies on the existence of common boundaries or points to detect neighboring regions. The Sakhalin and Kaliningrad regions, which are enclaves, are manually linked to a few nearest regions. Two remaining matrices treat regions belonging to the same upper-level macro-region as neighbors, and all other regions as non-neighbors. One of these matrices uses economic regions act as macro-regions, and the other uses federal districts. Economic regions are defined according to the classification that has been widely used by economic geographers and spatial development practitioners in Russia for decades, as outlined, for example, in [@Leyzerovich2010]. The composition of federal districts is defined by the Decree of the President of the Russian Federation (No. 849 of May 13, 2000) “On the Plenipotentiary Representative of the President of the Russian Federation in the Federal District”, with respective amendments.

A global Moran's *I* statistic [@Moran1948] is calculated for each combination of naming pattern and spatial weight matrix. The variable of interest is the proportion of law firm names that follow a pattern in a total set of law firm names in a region. If there are no law firm names of the pattern in the region, the proportion is considered to be zero. For those naming patterns where the global Moran's *I* is statistically significant, and this significance is robust, a local Moran's *I~i~* is calculated for each region. In addition, each region is categorised and labelled according to its value and the values of its neighbors. Four typical categories are used: “High-High” (high value in a region and its neighbors), “Low-Low” (an opposite), “Low-High”, “High-Low”. *P*-values are adjusted for multiple comparisons using Holm's correction [@Holm1979]. The significance level is set at 0.05.

### 2.3.6. Data statistics

@@

## 3.1. Law firms naming patterns and strategies

After clustering and manual grouping, 22 naming patterns are identified and assigned to one of four naming strategies (see Fig. 1 for a dendrogram and Table 1 for a complete list of clusters, their descriptions, patterns, and strategies). The most popular is the no-strategy followed by ~18, 700 law firms. Slightly less important is the belonging strategy with ~15, 000 companies. The uniqueness strategy (~8, 300 law firms) is relatively rare, and the least used is the market strategy (~5, 300 companies).

Belonging strategy includes law firms that directly state that they are law firms. “Law firm” is the most common pattern of this strategy. Most of the others (“Law”, “Lawyer”, “Legal service”) are semantically similar to it. It may seem questionable to include the “Personal brand” pattern (names such as “Mr. Brilliant and partners”) in this category, since personal branding also serves as a differentiation tool and thus implies uniqueness with the corresponding strategy. However, in Russia this way of naming is associated with lawyers, and such names often include the mention of law (“Law firm of Mr. Brilliant” instead of just “Mr. Brilliant”). In addition, Bassols i Gardella et al. [@BassolsiGardella2023] also categorise the personal branding of tourism firms as the belonging strategy.

Market strategy, according to the original definition, is used by firms “having a name directly appealing to markets” [@BassolsiGardella2023]. In the case of law firms, this can be achieved by mentioning target clients (“Business” pattern) or by using words with positive meanings that attract customers (“Positive”, “Plus”, “Legal aid”, “Guarantor” patterns). The “Expert” pattern is complex, as this word can be used to indicate either a high level of service (“expert” as a synonym for “professional”) or forensic services (“expert” as a forensic scientist). It is included here into market strategy because the semantic similarity of “experts” and “forensic scientists” in the Russian language is probably used as a marketing tool by forensic companies.

Uniqueness strategy encompasses law firms whose names mention a particular type of service (“Property&Development”, “Consulting”, “Audit&Finance”) or a specific geographical region (“Siberia”). In contrast to belonging, these firms usually do not indicate in their names that they are part of legal services market. The opposition between belonging and uniqueness strategies may reflect a division between general and specialised law firms. Patterns of this strategy have the potential to be used to identify the specialisation of law firms, although this requires an additional research.

No-strategy is a catch-all group for names that do not fit into any of the other three. Its main component is miscellaneous one-word names that are difficult to categorise or describe. This strategy also includes names containing the words “Group”, “Partnership”, “Center” or “Service” (usually without any meaningful clarification of the activity or type of service). The “Managing companies” pattern is, after some consideration, classified as no-strategy. In Russia, the term “managing companies” may define either property or asset management firms or house management companies, and although some of their services may be treated as paralegal, it is difficult to place them in either the belonging, uniqueness, or market strategy The same logic applies to the “EdSciTech” pattern with probably education or LegalTech companies.

@@

There are few patterns (3 out of 22) with statistically significant regularities in their spatial distribution (Fig. 2). These results are stable regardless of the technique used to construct the spatial weight matrix. The “Siberia” pattern is characterised by the highest global Moran's *I*, while the values for the “Expert” and “Personal brand” patterns are much lower, but still statistically significant.

A hotspot of the “Siberia” pattern is unsurprisingly located in Siberia (Fig. 3a). It includes four core regions (Novosibirsk, Tomsk, Kemerovo regions, Altai Territory) and a periphery of a few other regions (e.g. Omsk region, Republic of Khakassia, Republic of Altai). The hotspots of two other patterns (Fig. 3b, Fig. 3c) are located in the European South of Russia. This part of Russia is characterised by a mixture of regions where the popularity of a particular naming pattern is either high in a similar neighborhood or low in the neighborhood of regions with high values. This observation can be partly attributed to the presence of outliers among the national republics of the North Caucasus where the characteristics and composition of the legal services market differ significantly from their nearest neighbors. Some of these nearest neighbors (e.g. Krasnodar Territory) are, on the contrary, the regions with a relatively developed legal services market. In summary, the analysis and mapping of its results revealed two geographical parts of Russia where some naming patterns differ from the rest of the country: Siberia and the European South. However, the majority of naming patterns show no spatial regularities, i.e. their spatial distribution is not statistically significantly different from random.

@@

The findings of the study are somewhat contradictory. On the one hand, there are 22 law firm naming patterns in Russia that can be attributed to one of the four broad SMN strategies: belonging or uniqueness, market or no-strategy. Apart from the no-strategy (~40% of firms), belonging is the most popular strategy used by 30% of law firms, followed by uniqueness (~20%) and market (~10%). On the other hand, in gerenal there are no spatial regularities in the distribution of law firms that use a particular pattern: all the parts of the country are generally the same when it comes to law firms naming. Two notable exceptions to this rule are Siberia, with a fairly popular geographical branding (“Siberia” pattern), and the European South, with an unusual spatial composition of “Expert” and “Personal brand” patterns.

The contribution of this study is primarily theoretical and methodological in nature. It underscores the significance of firm names as a source of information for business- and economy-related research. It also proposes a technique for comprehensive analysis of branding in a geographical context through the use of modern natural language processing (NLP) solutions based on artificial neural networks. Additionally, it advocates for the utilization of disaggregated administrative open data for a spatial analysis. The findings demonstrate that even though the legal services market looks quite disconnected from the geography, the place can still play some role in its branding. Finally, the study provides an illustration of a semi-automated brand classification within a specific economic sector and discovers a geographical variation in naming strategies that could be further investigated.

@@

```{r fig-1-naming-patterns-and-strategies, fig.cap="**Fig 1.** Dendrogram of law firm naming patterns and strategies in Russia", fig.height=8}
names_classification_plot
```

```{r table-1-clusters}
kable(
  clusters_info_table,
  col.names = c(
    "# of cluster", "# of names", "Description",
    "Pattern", "Strategy"
  ),
  caption = "Table 1. Characteristics of clusters of law firm names"
)
```

```{r fig-2-global-moran-i, fig.cap="Fig. 2. Global Moran's *I* statistics and p-values for law firm naming patterns", fig.height=4}
moran_test_global_res_plot
```

```{r fig-3-localmoran-maps, fig.cap="Fig. 3. Maps of hotspots in the spatial distribution of three law firms naming patterns", fig.height=5}
localmoran_maps
```
